Elders Moisture Summary

### 2020-03-12 wood_moisture_summary.Rmd
plot and summary updates

---
title: "Elders Moisture Summary"
author: "Ethan Walker"
date: "Started 5 March 2020, Updated 10 March 2020"
output: pdf_document
---

@@

# Moisture content summary stats
## Average of 3 measurements
```{r}
moisture_n <- moisture_clean %>% 
  filter(winter_id == 1) %>% 
  group_by(area) %>%
  filter(!is.na(moisture_ave)) %>% 
  distinct(home) %>% 
  summarize(n())

summary_moisture <- moisture_clean %>%
  filter(winter_id == 1) %>% 
  group_by(area) %>% 
  summarize(mean = mean(moisture_ave, na.rm = TRUE), 
            SD = sd(moisture_ave, na.rm = TRUE),
            median = median(moisture_ave, na.rm = TRUE),
            min = min(moisture_ave, na.rm = TRUE), 
            max = max(moisture_ave, na.rm = TRUE)) %>%
  select(-area) %>% 
  t() 
kable(summary_moisture, col.names = c("Navajo", "Nez Perce"), 
      digits = 1, align = "c")

summary_moisture <- moisture_clean %>%
  filter(winter_id == 1) %>% 
  summarize(mean = mean(moisture_ave, na.rm = TRUE), 
            SD = sd(moisture_ave, na.rm = TRUE),
            median = median(moisture_ave, na.rm = TRUE),
            min = min(moisture_ave, na.rm = TRUE), 
            max = max(moisture_ave, na.rm = TRUE)) %>%
  t() 
kable(summary_moisture, digits = 1, align = "c")
```

@@

# Boxplots
```{r, fig.height=6, fig.width=5}
boxplots_moisture <- moisture_clean %>% 
  filter(winter_id == 1) %>% 
  select(area, moisture_ave) %>% 
  na.exclude() %>% 
  ggplot(aes(area, moisture_ave)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=3, color="red") +
    theme_minimal() +
    ylim(0, 50) +
    #geom_hline(yintercept = 50, color = "red", size = 1.2) +
    labs(y = "Mean moisture content (%)") +
    #labs(aes(x = "", y = paste("48-hour indoor PM "[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_moisture
```

#### Abstract/manuscript tables ####

# Filter for homes that have PM data
```{r}
# 93 Winter 1 placebo homes have PM data
pm_homes <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  group_by(area, home, sampling_visit) %>% 
  mutate(initial_obs = if_else(pm_datetime_new == first_datetime, 1, 0)) %>% 
  filter(initial_obs == 1) %>% 
  mutate(pm_home = "true") %>% 
  select(area, home, home_winter_id, sampling_visit, pm_home, first_datetime) %>% 
  separate(first_datetime, c("first_date", "first_time"), sep = " ", remove = TRUE) %>% 
  ungroup() %>% 
  arrange(area, home)

@@

# Summarize home data
```{r}
# Summarize numeric vars
kids_moisture <- moisture_filtered_time %>%  
  group_by(area) %>% 
  summarize("Mean" = mean(moisture_ave, na.rm = TRUE), 
            "SD" = sd(moisture_ave, na.rm = TRUE),
            "min" = min(moisture_ave, na.rm = TRUE), 
            "med" = median(moisture_ave, na.rm = TRUE), 
            "max" = max(moisture_ave, na.rm = TRUE))
kable(kids_moisture, digits = 1, align = "c")

# Summarize numeric vars
kids_moisture <- moisture_filtered_time %>%  
  #group_by(area) %>% 
  summarize("Mean" = mean(time_diff, na.rm = TRUE), 
            "SD" = sd(time_diff, na.rm = TRUE),
            "min" = min(time_diff, na.rm = TRUE), 
            "med" = median(time_diff, na.rm = TRUE), 
            "max" = max(time_diff, na.rm = TRUE))
kable(kids_moisture, digits = 1, align = "c")
```

>>>>

---
title: "Elders Moisture Summary"
author: "Ethan Walker"
date: "Started 5 March 2020, Updated 12 March 2020"
output: pdf_document
---

@@

```{r}
# Moisture content summary stats
## Average of 3 measurements

moisture_n <- moisture_clean %>% 
  filter(winter_id == 1) %>% 
  group_by(area) %>%
  filter(!is.na(moisture_ave)) %>% 
  distinct(home) %>% 
  summarize(n())
```

# Moisture content by area
```{r}
summary_moisture <- moisture_clean %>%
  filter(winter_id == 1) %>% 
  group_by(area) %>% 
  summarize(mean = mean(moisture_ave, na.rm = TRUE), 
            SD = sd(moisture_ave, na.rm = TRUE),
            median = median(moisture_ave, na.rm = TRUE),
            min = min(moisture_ave, na.rm = TRUE), 
            max = max(moisture_ave, na.rm = TRUE)) %>%
  select(-area) %>% 
  t() 
kable(summary_moisture, col.names = c("Navajo", "Nez Perce"), 
      digits = 1, align = "c")
```

# Moisture content total
```{r}
summary_moisture <- moisture_clean %>%
  filter(winter_id == 1) %>% 
  summarize(mean = mean(moisture_ave, na.rm = TRUE), 
            SD = sd(moisture_ave, na.rm = TRUE),
            median = median(moisture_ave, na.rm = TRUE),
            min = min(moisture_ave, na.rm = TRUE), 
            max = max(moisture_ave, na.rm = TRUE)) %>%
  t() 
kable(summary_moisture, digits = 1, align = "c")
```

@@

```{r, fig.height=6, fig.width=5}
boxplots_moisture <- moisture_clean %>% 
  filter(winter_id == 1) %>% 
  select(area, moisture_ave) %>% 
  na.exclude() %>% 
  ggplot(aes(area, moisture_ave)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red",
                 position=position_nudge(x = -0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=mean, geom="text", 
                 size=7, position=position_nudge(x = -0.35, y = 0)) +
    stat_summary(fun.y=median, geom="point", shape=16, size=4, color="blue",
                 position=position_nudge(x = 0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=median, geom="text", 
                 size=7, position=position_nudge(x = 0.35, y = 0)) +
    theme_minimal() +
    ylim(0, 50) +
    #geom_hline(yintercept = 50, color = "red", size = 1.2) +
    labs(title = "Mean wood moisture content" , y = "%") +
    #labs(aes(x = "", y = paste("48-hour indoor PM "[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          title = element_text(size = 18, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_moisture
```

```{r}
#### Abstract/manuscript tables ####

# Filter for homes that have PM data

pm_homes <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  group_by(area, home, sampling_visit) %>% 
  mutate(initial_obs = if_else(pm_datetime_new == first_datetime, 1, 0)) %>% 
  filter(initial_obs == 1) %>% 
  mutate(pm_home = "true") %>% 
  select(area, home, home_winter_id, sampling_visit, pm_home, first_datetime) %>% 
  separate(first_datetime, c("first_date", "first_time"), sep = " ", remove = TRUE) %>% 
  ungroup() %>% 
  arrange(area, home)

@@

```{r, include=FALSE}
# Summarize numeric vars
elders_moisture <- moisture_filtered_time %>%  
  group_by(area) %>% 
  summarize("Mean" = mean(moisture_ave, na.rm = TRUE), 
            "SD" = sd(moisture_ave, na.rm = TRUE),
            "min" = min(moisture_ave, na.rm = TRUE), 
            "med" = median(moisture_ave, na.rm = TRUE), 
            "max" = max(moisture_ave, na.rm = TRUE))
kable(elders_moisture, digits = 1, align = "c")

# Summarize numeric vars
elders_moisture <- moisture_filtered_time %>%  
  #group_by(area) %>% 
  summarize("Mean" = mean(time_diff, na.rm = TRUE), 
            "SD" = sd(time_diff, na.rm = TRUE),
            "min" = min(time_diff, na.rm = TRUE), 
            "med" = median(time_diff, na.rm = TRUE), 
            "max" = max(time_diff, na.rm = TRUE))
kable(elders_moisture, digits = 1, align = "c")
```
